### 2019-07-01 README.Rmd
Fixed github_document equation rendering
Added diffEnrich step to README

---
output: github_document
always_allow_html: yes
---

@@

>>>>

---
output: 
  github_document:
    pandoc_args: --webtex
always_allow_html: yes
---

@@

### Step 3: Identify differentially enriched KEGG pathways

The diffEnrich function will merge the results from the *pathEnrich* calls generated above. Specifically, the dataframe
'sig_pe' and the dataframe 'bkg_pe' will be merged using the base *merge* functionality and be merged by the following columns:
'c("KEGG_ID", "KEGG_description", "KEGG_cnt", "numTested")'. This merged data set will then be used to perform differential 
enrichment usng the same method and p-value calculation as described above.

```{r diffEnrich}
## Perform differential enrichment
diff_enrich <- diffEnrich(sig_pe = sig_pe, bkg_pe = bkg_pe)

knitr::kable(head(diff_enrich),
             caption = "Table 2. Description of columns is dataframe generated by pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

The result of the *diffEnrich* call is the merged dataframe with the estimated odds ration generated by the Fisher's Exact test 
and the associated p-value.
